Grade Retention and Mixed Race

### 2022-09-05 products/paper/main.qmd
Simplify descriptive stat table; Add resource difference table

```{r load-data}
load(here("analysis","output","acs.RData"))
load(here("analysis","output","coef_table.RData"))
load(here("analysis","output","monoracial_results.RData"))
# change names of models for display
coef_table <- coef_table %>%
  mutate(model=factor(model,
                      levels=c("crude","fixed effects","cultural resources",
                               "parent resources"),
                      labels=c("Raw","Baseline model","Cultural model",
                               "Full model")))
```

@@

```{r}
#| label: tbl-descriptive
#| tbl-cap: Descriptive statistics by race. Shading indicates biracial group. Groups ordered by sample size.
tbl_summary <- acs %>%
  group_by(race) %>%
  summarize(n=n(), 
            held_back=percent(mean(below_exp_grade), accuracy=0.01),
            mean_age=round(mean(age), 1),
            f_born=percent(mean(foreign_born),  accuracy=0.1),
            par_fb=percent(mean(foreign_born_father | 
                                  foreign_born_mother), accuracy=0.1),
            fam_inc=dollar(round(mean(family_income), 0)),
            own_home=percent(mean(own_home), accuracy=0.1),
            par_ba=percent(mean(degree_father=="BA" | 
                                  degree_father=="G" | 
                                  degree_mother=="BA" | 
                                  degree_mother=="G"), accuracy=0.1)
  ) %>%
  arrange(desc(n)) %>%
  mutate(n=comma(n))

@@

tbl_summary %>%
  kbl(booktabs = TRUE,
      linesep = NULL,
      align = c("l",rep("r", ncol(tbl_summary)-1)),
      col.names=c("race",
                  "n",
                  "clearly below expected grade", 
                  "mean age",
                  "foreign-born",
                  "either parent foreign-born",
                  "mean family income",
                  "own home",
                  "either parent, college degree"
      )) %>%
  kable_styling(font_size=8) %>%
  column_spec(3:10, width = "1.2cm") %>%
  row_spec(index_biracial, background = "#D3D3D3")
#%>% landscape()
```

@@

g+annotate("text", 1, 0.035, hjust="left",
             label="Grey bands give 83.4%\nconfidence interval around\nmonoracial estimates")+
  annotate("text", 2, 0.045, hjust="left",
             label="Red band gives 83.4%\nconfidence interval around\nmidpoint estimate")+
  annotate("text", 2.5, 0.036, hjust="left",
             label="Actual biracial estimate\nshown with 83.4% confidence\ninterval")
```

@@

@@

```{r monoracial-results}
#| results: asis
#| label: tbl-monoracial
#| tbl-cap: Average marginal differences in the probability of being behind grade by monoracial group, relative to a monoracial white student
texreg(map(results_monoracial, convert_marg),
       digits=3,
       caption = "Average marginal differences in the probability of being clearly behind grade by monoracial group, relative to a monoracial white student",
       caption.above=TRUE,
       label="tbl-monoracial",  #TODO: This does not work
       float.pos="t",
       custom.gof.rows=
         list("State fixed effects" = c("Yes","Yes","Yes","Yes"),
              "Location fixed effects" = c("Yes","Yes","Yes","Yes"),
              "Grade fixed effects" = c("Yes","Yes","Yes","Yes"),
              "Year linear effects" = c("Yes","Yes","Yes","Yes"),
              "Year x grade effects"  = c("Yes","Yes","Yes","Yes"),
              "Nativity and language" = c("No","Yes","Yes","Yes"),
              "Parent's education" = c("No","No","Yes","Yes"),
              "Family resources" = c("No","No","No","Yes")))
```

>>>>

```{r load-data}
load(here("analysis","output","acs.RData"))
load(here("analysis","output","coef_table.RData"))
load(here("analysis","output","monoracial_results.RData"))
load(here("analysis","output","tbl_resources.RData"))
# change names of models for display
coef_table <- coef_table %>%
  mutate(model=factor(model,
                      levels=c("crude","fixed effects","cultural resources",
                               "parent resources"),
                      labels=c("Raw","Baseline model","Cultural model",
                               "Full model")))
# create design object
acs_design <- acs %>%
  as_survey_design(ids = cluster, weights = perwt)
```

@@

```{r}
#| label: tbl-descriptive
#| tbl-cap: Descriptive survey-weighted statistics by race. Shading indicates biracial group. Groups ordered by sample size.
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(n=n(), 
            held_back=percent(as.numeric(survey_mean(below_exp_grade, 
                                                     vartype=NULL)), 
                              accuracy=0.01),
            mean_age=round(survey_mean(age, vartype=NULL), 1)) %>%
  arrange(desc(n)) %>%
  mutate(n=comma(n))

@@

tbl_summary %>%
  kbl(booktabs = TRUE,
      linesep = NULL,
      align = c("l",rep("r", ncol(tbl_summary)-1)),
      col.names=c("race",
                  "n",
                  "clearly below expected grade", 
                  "mean age" )) %>%
  kable_styling() %>%
  row_spec(index_biracial, background = "#D3D3D3")
```

@@

g+annotate("text", 1, 0.036, hjust="left",
             label="Grey bands indicate 83.4%\nconfidence interval around\nmonoracial estimates")+
  annotate("text", 2, 0.0445, hjust="left",
             label="Red band indicate 83.4%\nconfidence interval around\nmidpoint estimate")+
  annotate("text", 2.5, 0.0365, hjust="left",
             label="Actual biracial estimate\nshown with 83.4%\nconfidence interval")
```

@@

## Monoracial Differences

@@

```{r monoracial-results}
#| results: asis
#| label: tbl-monoracial
#| tbl-cap: Average marginal differences in the probability of being behind grade by monoracial group, relative to a monoracial white student
texreg(map(results_monoracial[-1], convert_marg),
       digits=3,
       caption = "Average marginal differences in the probability of being clearly behind grade by monoracial group, relative to a monoracial white student",
       caption.above=TRUE,
       label="tbl-monoracial",  #TODO: This does not work
       float.pos="t",
       custom.gof.rows=
         list("State fixed effects" = c("Yes","Yes","Yes","Yes"),
              "Location fixed effects" = c("Yes","Yes","Yes","Yes"),
              "Grade fixed effects" = c("Yes","Yes","Yes","Yes"),
              "Year linear effects" = c("Yes","Yes","Yes","Yes"),
              "Year x grade effects"  = c("Yes","Yes","Yes","Yes"),
              "Nativity and language" = c("No","Yes","Yes","Yes"),
              "Parent's education" = c("No","No","Yes","Yes"),
              "Family resources" = c("No","No","No","Yes")))
```

## Resource Differences by Race

```{r}
#| label: tbl-resources
#| tbl-cap: Mean resources by racial group. All results are survey weighted. Results sorted by counterfactual probability of grade retention. Shading indicates biracial group.
index_biracial <- which(str_detect(tbl_resources$race, "/"))

tbl_resources %>%
  select(race, held_back_cf, fam_inc, own_home, m_ba, f_ba, f_born, par_fb,
         spk_eng_well, spk_eng_par) %>%
  mutate(held_back_cf=percent(held_back_cf/100, accuracy=0.1),
         own_home=percent(own_home/100, accuracy=0.1),
         m_ba=percent(m_ba/100, accuracy=0.1),
         f_ba=percent(f_ba/100, accuracy=0.1),
         f_born=percent(f_born/100, accuracy=0.1),
         par_fb=percent(par_fb/100, accuracy=0.1),
         spk_eng_well=percent(spk_eng_well/100, accuracy=0.1),
         spk_eng_par=percent(spk_eng_par/100, accuracy=0.1),
         fam_inc=dollar(fam_inc)) %>%
  kbl(booktabs = TRUE,
      linesep = NULL,
      align = c("l",rep("r", ncol(tbl_resources)-1)),
      col.names=c("race","held back, counterfactual","family income",
                  "own home","mother, 4-year college degree",
                  "father, 4-year college degree",
                  "foreign-born","either parent foreign-born",
                  "speak English well", 
                  "Both parents speak english well")) %>%
  kable_styling() %>%
  row_spec(index_biracial, background = "#D3D3D3") %>%
  column_spec(2:10, width = "1.5cm") %>%
  landscape()
```

## Biracial Placement
